---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dietrecallkit

<!-- badges: start -->
<!-- badges: end -->

**dietrecallkit** provides tools to clean, process, and generate indicators from dietary recall data. It is designed to handle raw recall tables and their linked food details, ensuring reproducible workflows for nutrition research.

## Installation

You can install the development version of dietrecallkit from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("tosmartak/dietrecallkitR")
```

## Example

The package comes with a lightweight, relational example dataset called dietrecall_example. This dataset contains three linked tables: `maintable`, `food_details`, and `food_ingredients_group` similar to what you would have when you used the dietary recall questionnaire from the 24hour recall toolkit.

Note: the dataset is just a sample and not a real dataset and must be loaded explicitly with data() since LazyData is set to false”

```{r example}
library(dietrecallkit)

# Load the example dataset
data("dietrecall_example")

# Explore maintable
head(dietrecall_example$maintable)

# Linked food details
head(dietrecall_example$food_details)
```


## Contributing
We welcome contributions! Please see the issues page for ideas or open a new issue.
