---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dietrecallkit Package - R

<!-- badges: start -->
[![License: GPL v2 or later](https://img.shields.io/badge/License-GPL%20v2%2B-blue.svg)](https://www.gnu.org/licenses/old-licenses/gpl-2.0.html)
<!-- badges: end -->

**dietrecallkit** is a cross-platform package designed to enhance the efficiency of researchers and analysts in cleaning, processing, and calculating complex dietary and nutrient indicators from dietary recall data. Built for both **Python** and **R**, it provides tools to streamline workflows, ensuring accurate and reproducible results in dietary and nutrition-related studies.

---

## **Key Features**
- Efficient cleaning of data collected using the built in XLSForm
- Efficient computation of nutrient and dietary indicators.
- Compatible with **Python** and **R**, catering to a wide range of researchers. ([See Python Repository](https://github.com/tosmartak/dietrecallkitPy))
- Designed for reproducibility and accuracy in research.
- Simplifies complex calculations, saving time and effort.

---

## **Who Is This For?**
- **Nutrition Researchers**: Calculate indicators for dietary assessments with ease.
- **Data Analysts**: Streamline workflows for nutrient analysis.
- **Academics and Students**: Learn and apply dietary metrics in a research-ready framework.

---


## Installation in R

You can install the development version of dietrecallkit from [GitHub](https://github.com/tosmartak/dietrecallkitR) with:

``` r
# install.packages("pak")
pak::pak("tosmartak/dietrecallkitR")
```

or install from R-CRAN with

```r
install.packages("dietrecallkit")
```

## Quick Start

### Example

The package comes with a lightweight, relational example dataset called dietrecall_example. This dataset contains three linked tables: `maintable`, `food_details`, and `food_ingredients_group` similar to what you would have when you used the dietary recall questionnaire from the 24hour recall toolkit.

Note: the dataset is just a sample and not a real dataset and must be loaded explicitly with data() since LazyData is set to false”. Ideally this should be replaced with your own dataset

```{r example, eval=FALSE}
# Load the package after installation
library(dietrecallkit)

# Load the example dataset
data("dietrecall_example")

# Explore maintable
head(dietrecall_example$maintable)

# Linked food details
head(dietrecall_example$food_details)

# Linked food ingredient
head(dietrecall_example$food_ingredients_group)
```


---

## **Contributing**
Contributions are welcome! If you'd like to contribute, please:

1. Fork the repository.
2. Create a feature branch (`git checkout -b feature-name`).
3. Commit your changes (`git commit -m 'Add a new feature'`).
4. Push to the branch (`git push branch-name feature-name`).
5. Create a pull request.

---

## **License**
`dietrecallkit` package is licensed under the [GNU General Public License (GPL) version 2 or later](https://www.gnu.org/licenses/old-licenses/gpl-2.0.html).

---

## **Acknowledgments**
Special thanks to all the contributors and users who have supported the development of this package.

---

## **Contact**
For questions or feedback, please reach out at [t.akingbemisilu@cgiar.org].

